Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
Updated experimental section text.

\textcolor{red}{How did you obtain the results from Table~\ref{tab:results}? 
Can you provide the command-line? The reviewers should be able to reproduce our experiments.}
We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. \textcolor{red}{Which section do you refer??
For most benchmarks the conjecture explained in section~\ref{fixedpoint_verification} 
holds and the inductive back-end is able to find a stable solution in less than one minute}. 
This is possible if the inductive solutions need to be refined with few counterexamples 
and fixed point precision increases. However, some of our benchmarks did not meet these criteria. 
\textcolor{red}{Which cases? Can you refer to Table~\ref{tab:results} In these cases, 
the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes}.

@@

\textcolor{red}{Can you provide the synthesised controllers? Iury could then check the solution using the bode diagram.}
We conclude from these results that the inductive back-end provides excellent performance
for synthesising stable controllers in the majority of the benchmarks \textcolor{red}{can you be more specific? which benchmarks?}, and can be
complemented using the interval arithmetic back-end, where the inductive conjectures fail
too frequently. Both back-ends enabled controller synthesis for all benchmarks within
reasonable time frames.

>>>>

\textcolor{red}{How did you obtain the results from Table~\ref{tab:results}? 
Can you provide the command-line? The reviewers should be able to reproduce our experiments.}
We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. \textcolor{red}{Which section do you refer??
For most benchmarks the conjecture explained in section~\ref{fixedpoint_verification} 
holds and the inductive back-end is able to find a stable solution in less than one minute}. 
This is possible if the inductive solutions need to be refined with few counterexamples 
and fixed point precision increases. However, two benchmarks in our set did not meet these
criteria (marked with $^*$ in Table~\ref{tab:results}). In these cases, 
the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.

@@

\textcolor{red}{Can you provide the synthesised controllers? Iury could then check the solution using the bode diagram.}
We conclude from these results that the inductive back-end provides excellent performance
for synthesising stable controllers in the 12 out of 14 benchmarks, and can be
complemented using the interval arithmetic back-end for the remaining 2 benchmarks,
where the inductive conjectures fail too frequently. Both back-ends together enabled controller
synthesis for all benchmarks within reasonable time frames.
